Supplementary Information: Tropical tree drought sensitivity is jointly shaped by drought characteristics, species adaptations, and individual microenvironments

### 2025-06-26 doc/manuscript_hkk_drought_sensitivity.Rmd
update Fig. 1 caption
#10

***Figure `r fig_droughts`. Climatic characteristics of the focal drought years (black in 2010, purple in 2015, orange in 2020) compared with the average across years*** 2008-2019 (grey dashed) and its standard deviation (grey shading) in the Huai Kha Khaeng ForestGEO plot, for four daily climate variables: dry days, precipitation, maximum temperature and VPD.  (a) 30-day running means. (b) Anomalies of the drought year running means from the averages, in units of standard deviations.  (c) Standardised Precipitation Evapotranspiration Index (SPEI) values for the drought years at four different time scales for each month for each drought year. A k-month SPEI integrates over k months ending in the month current month. Across all panels, light blue background represents the average wet-season, from May to October.

>>>>

***Figure `r fig_droughts`. Climatic characteristics of the focal drought years compared with the average across years*** in the Huai Kha Khaeng ForestGEO plot, for four daily climate variables: dry days, precipitation, maximum temperature and VPD.  (a) 30-day running means. (b) Anomalies of the drought year running means from the 2008-2019 averages, in units of standard deviations.  (c) Standardised Precipitation Evapotranspiration Index (SPEI) values for the drought years at four different time scales for each month for each drought year. A k-month SPEI integrates over k months ending in the month current month. Across all panels, light blue background represents the average wet-season, from May to October.
